Efficient Coalition Formation for Web Services

### 2013-03-03 papers/coalition/coalition.tex
Changes

In this scenario, there are is a community controller by its master web sercice. The community master has some request rate $(R_{master})$ from users. Web services need to join a community to be able to get tasks from a master web service. Each web service comes with different quality of service patameters and a throughput $(T_ws)$. Throughput is the average rate of tasks a web service can perform. Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with some QoS output metrics and a rate or $T_{ws}$. 
In this setting, we define the value of the coalition as follows:
\begin{equation*}
output(C) = \sum_{ws}{(T_{ws} \times QoS_{ws})}
\end{equation*}

@@

The membership decision is made based on throughput and QoS of the requested web service. The goal is to have quality web services in community so the community stays stable and no other web services would have incentives to deviate and join ``other'' coalitions. Therefore, we it check the core membership of the coalition of all current community members and the new web service. Our algorithm uses the shapley value distribution method as described in equation \ref{eq:shapley} to distribute gain of $v(C)$ among all members and then checks if shapley value payoff vector for this community having characteristic function $v(C)$ is Core stable or not. In shapley value payoff vector, the payoff for each web service i, is calculated based on their contribution $v(C \cup {i}) - v(C)$ and then averaging over the possible different permutations in which the coalition can be formed. It is proven in \cite{DBLP:conf/ijcai/GrecoMPS11} if the Core is non-empty, the shapley payoff vector is a member of Core, so in our algorithm we check the core membership of this payoff vector.

>>>>

In this scenario, there are is a community controller by its master web sercice. The community master has some request rate $(R_{master})$ from users. Web services need to join a community to be able to get tasks from a master web service. Each web service comes with different quality of service patameters and a throughput $(T_{ws})$. Throughput is the average rate of tasks a web service can perform. Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with some QoS output metrics and a rate or $T_{ws}$. 
In this setting, we define the value of the coalition as follows:
\begin{equation*}
output(C) = \sum_{ws}{(T_{ws} \times QoS_{ws})}
\end{equation*}

@@

The membership decision is made based on throughput and QoS of the requested web service. The goal is to have quality web services in community so the community stays stable and no other web services would have incentives to deviate and join ``other'' coalitions. Therefore, we it check the core membership of the coalition of all current community members and the new web service. Our algorithm uses the shapley value distribution method as described in equation \ref{eq:shapley} to distribute gain of $v(C)$ among all members and then checks if shapley value payoff vector for this community having characteristic function $v(C)$ is Core stable or not. In shapley value payoff vector, the payoff for each web service i, is calculated based on their contribution $v(C \cup {i}) - v(C)$ and then averaging over the possible different permutations in which the coalition can be formed. It is proven in convex games the Shapley value lies in the core \cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}. Therefore if the Core is non-empty, the Shapley payoff vector is a member of Core, so in our algorithm we check the core membership of this payoff vector.
